Is the direction of Granger causal influence the same as the direction of information flow?

### 2015-07-07 paper.tex
Add SK block diagram figure.

\section{A simple feedback communication scheme}
\label{sec:sk}
This section summarizes the analysis in the work of Schalkwijk and Kailath~\cite{S&K}, and a simple (and previously known) extension to a noisy feedback case. It also establishes the model and the notation used in the paper.

@@

Suppose we try to use the Granger causality measure of directed influence to infer the direction of information flow. As discussed in Section~\ref{sec:intro}, one might expect the direction of information flow --- and hence the direction of greater Granger causality --- to be from the transmitter to the receiver.

>>>>

\section{A simple feedback communication scheme}
\label{sec:sk}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.2in]{sk-block-diagram}
	\caption{A block-diagram representation of the communication system, describing the feedback channels and supplying notation for the variables used throughout the paper.}
	\label{fig:sk-block-diagram}
\end{figure}

This section summarizes the analysis in the work of Schalkwijk and Kailath~\cite{S&K}, and a simple (and previously known) extension to a noisy feedback case. It also establishes the model and the notation used in the paper.

@@

Suppose we try to use the Granger causality measure of directed influence to infer the direction of information flow. As discussed in Section~\ref{sec:intro}, one might expect the direction of information flow -- and hence the direction of greater Granger causality -- to be from the transmitter to the receiver.
